Optimizing the Robotics Closet

### 2018-11-16 paper.tex
references

\section{Related Work}
Deepesh Singh's \emph{A Beginner’s guide to Shelf Space Optimization using Linear Programming}
explains an integer programming formulation for finding the optimal layout of a store
that maximizes sales. The guide organizes the store into several racks, each with
a certain number of shelves. One key assumption is that only one product can fit
on a rack. The model uses a table showing how many sales are generated by each item
depending on which rack it is placed. The objective function is then the profit
generated by a given arrangement. Arrangements are represented by a matrix, with
each $a_{ij}$ representing whether product $j$ is on shelf $i$. If it is, the
$a_{ij}$ is $1$ and $0$ otherwise. The guide shows how to maximize this profit function.
Although this approach is a good start, our problem differs in several ways: we can
fit more than one box on each shelf, and our goal is to minimize time of retrieval
rather than maximize profits.

@@

\section{Acknowledgements}
We would like to thank:
\begin{itemize}
\item Dr. Sara Billey for providing us with guidance throughout the project,
\item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
\item UW Husky Robotics for providing the closet to undergo optimization,
\item Nolan Donovan for working with us to understand and solve this problem.
\end{itemize}
\end{document}

>>>>

\section{Related Work}
Deepesh Singh's \emph{A Beginner’s guide to Shelf Space Optimization using Linear Programming}
\cite{india} explains an integer programming formulation for finding the optimal layout
of a store that maximizes sales. The guide organizes the store into several racks, each
with a certain number of shelves. One key assumption is that only one product can fit
on a rack. The model uses a table showing how many sales are generated by each item
depending on which rack it is placed. The objective function is then the profit
generated by a given arrangement. Arrangements are represented by a matrix, with
each $a_{ij}$ representing whether product $j$ is on shelf $i$. If it is, the
$a_{ij}$ is $1$ and $0$ otherwise. The guide shows how to maximize this profit function.
Although this approach is a good start, our problem differs in several ways: we can
fit more than one box on each shelf, and our goal is to minimize time of retrieval
rather than maximize profits.

@@

\section{Acknowledgements}
We would like to thank:
\begin{itemize}
\item Dr. Sara Billey for providing us with guidance throughout the project,
\item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
\item Husky Robotics for providing the closet to undergo optimization,
\item Nolan Donovan for working with us to understand and solve this problem.
\end{itemize}

\section{References}
\begin{thebibliography}{9}
\bibitem{volleyball} Guido Cocchi, Alessandro Galligari, Federica Picca Nicolino,
  Veronica Piccialli, Fabio Schoen, Marco Sciandrone.
  “Scheduling the Italian National Volleyball Tournament.” Interfaces 48(3):271-284, 2018. 
\bibitem{india} Singh, Deepesh. “A Beginner’s guide to Shelf Space Optimization using
  Linear Programming.” Analytics Vidhya, 2016
\bibitem{knapsack} Andrea Lodi, Michele Monaci. “Integer Linear Programming Models for
  2-staged Two-Dimensional Knapsack Problems.” Dipartimento di Elettronica,
  Informatica e Sistemistica, University of Bologna, 2001
\bibitem{imnotamonkeyimascientist} Winston, Wayne. “Operations research:
  Applications and algorithms.” Belmont, CA: Thomson/Brooks/Cole, 2004
\bibitem{siggraph}  Yu, Lap-Fai, et al. “Make It Home.” ACM SIGGRAPH 2011 Papers
  on - SIGGRAPH 11, 2011, doi:10.1145/1964921.1964981.  
\end{thebibliography}
\end{document}
